\chapter{Preface}
This book is a selection of notes from twelve of the lectures
that I use in my year-round math olympiad classes.
The program is affectionately named OTIS.
The abbreviation officially stands for
``Olympiad Training for Individual Study'';
but in truth, I rigged the acronym so that it would match
the name of an elevator in Lincoln, Nebraska
of which I had fond childhood memories.

When I started teaching OTIS back in the fall of 2015,
it was just a small group of students at Phillips Academy
that I would meet with every couple of weeks.
Despite my inexperience at the time,
I have fond memories of this first group,
and I maybe learned as much from them as they did from me.

Every year since then, the number of OTIS students has doubled,
and the number of applications has increased even faster than that.
At the same time, I became increasingly involved
with volunteering with the organization of high-school contests.
By the time I started graduate school,
I was spending so little time on my own studies that
I began to fear (rightly or wrongly)
that I might fail out of the math PhD program.

Thus, despite my best efforts, I eventually had the
heartbreaking task of having to tell eager and
enthusiastic students that I simply did not have the time
or space to take them all under my wing.
I am the kind of person who finds it hard to say no,
and so this was painful for me to do.
OTIS taught me the reality that I am just one person.

In this way, these notes are an apology to everyone I turned down,
and to everyone that I will have to turn down.
I would have loved to be able to help everyone who came to my doorstep.
I am sorry that I could not do more,
but I wrote you a short book, as it was the least I could do.

As with all my works, there are bound
to be numerous errors, mistakes, or points of unclarity.
Comments, suggestions, corrections are very welcome.
You can reach me at \texttt{evan@evanchen.cc}.

\begin{flushright}
	Evan Chen \\
	December 30, 2018 \\
	Fremont, California, USA
\end{flushright}
